Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-03-11 manuscript/supplementaryRW.Rmd
update results of lm between complexity and overestimation

Table 1: Parameter settings associated with vegetation establishment.

![](images/image-1265081375.png)

@@

## Recruitment levels

@@

kable(zeroInflated,  format = "latex", caption = "Number of total samples, samples with zero recruitment and the proportion of zero recruitment per model and observed data.")|>
        kableExtra::landscape() |>
        kableExtra::kable_styling(full_width = F, latex_options = "scale_down")
```

## Model complexity

Summary of the linear model of the overestimation proportions versus the
mean complexity value on the establishment module.

```{r tableComp, echo=FALSE,  message=FALSE, render = 'normal_print'}
library(knitr)

tableCompOver <- readr::read_csv(here::here("figures", "tableCompOver.csv"))
jtools::summ(lm(overestimation ~ complexity, data = tableCompOver), model.info = FALSE, digits = 5)

>>>>

@@

## Ingrowth levels, tree diversity and mortality in tree establishment

kable(zeroInflated,  format = "latex", caption = "Number of total samples, samples with zero recruitment and the proportion of zero recruitment per model and observed data.")|>
        #kableExtra::landscape() |>
        kableExtra::kable_styling(full_width = F, latex_options = "scale_down")
```
## Model traits and model performance

### Model complexity VS overestimation

```{r plotComp, echo=FALSE, warning=FALSE, fig.cap="Plot and summary atatiatics of the linear model between the overestimation proportion in ingrowth levels and the mean complexity value of the establisment modules", fig.show = 'hold', out.width = '70%'}
tableCompOver <- readr::read_csv(here::here("figures", "tableCompOver.csv"))

ggplotRegression <- function(fit){
require(ggplot2)
ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "blue") +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}

fit1 <- lm(overestimation ~ complexity, data = tableCompOver)
ggplotRegression(fit1)

## Total ingrowth and individual species regeneration niches

@@
